### 2020-06-01 paper.tex
Add Experimental Scheme Subsection

Insert I/O here

>>>>

On one hand, the input arguments to the proposed algorithm implementation are the number of cells in the circuit with a maximum value of 52 and the population size used in the genetic algorithm. On the other hand, output parameters are the initial placement wirelength, the results of the simulated annealing algorithm runs, the result of a regular genetic algorithm with a randomly generated population, and finally, the result of the proposed algorithm.
